### 2014-02-15 paper/main.tex
minor updates

Although the unimodal assumption, A1, will not apply to all situations, we argue that it will be reasonable in many practical contexts. 
For example, in contexts where interest focusses on which $\beta_j$ differ from zero, which suggests that ``$\beta_j=0$" is a plausible null hypothesis,  
it seems reasonable to expect that ``$\beta_j$ very near 0" is also plausible, and that the distribution of the effects will be unimodal about 0. 
Alternatively, we can motivate A1 by its effect on point estimates, which is to ``shrink" the estimates towards the mode - 
such shrinkage is desirable from several standpoints for improving estimation accuracy. 
Interestingly, although the unimodal assumption for $g$ seems natural to us, much previous related work on estimating False Discovery Rates  
has assumed, either explicitly or implicitly, that the effect sizes are multimodal. (In contrast, almost all analogous work in large-scale regression assumes
unimodal distributions for the effect sizes, such as the spike and slab, Laplace, $t$, normal-gamma, normal-inverse-gamma, or horseshoe priors.)
We discuss the effects of these assumptions later. For now, it is important to note that assumption A1 relates to the distribution of {\it all} effects, and not only the {\it detectable} effects (i.e.~those that are significantly different from zero). It is very likely that the distribution of {\it detectable} non-zero effects will be multimodal, with one mode for detectable positive effects and another for detectable negative effects, and A1 does not contradict this.

Assumption A2 can be motivated by assuming that a) $\hat\beta_j, s_j$ contain most of the information about $\beta_j$ in the data $D_j$ (i.e. they are
``approximately sufficient" for $D_j$) and that b) $s_j$ alone contains little information about $\beta$. The former (a) suggests the approximation $\hat{L}_j(\beta_j) \propto p(\hat\beta_j, s_j | \beta) = p(\hat\beta | \beta, s_j) p(s_j | \beta)$, while the latter (b) suggests assuming that $p(s_j|\beta_j)$ does not depend on $\beta_j$. Putting these two together yields $\hat{L}_j(\beta_j) \propto p(\hat\beta_j | \beta, s_j)$, which, from (\ref{eqn:betahat}),  implies A2. (If $\hat\beta_j, s_j$ are not sufficient for $D_j$ then there is some loss of efficiency in making this approximation, but all Bayesian inferences remain valid provided they are interpreted as conditional on $\hat\beta_j,s_j$, rather than conditional on $D_j$.)

>>>>

Although the unimodal assumption, A1, will not apply to all situations, we argue that it will be reasonable in many practical contexts. 
For example, in contexts where interest focusses on which $\beta_j$ differ from zero, which suggests that ``$\beta_j=0$" is a plausible null hypothesis,  
it seems reasonable to expect that ``$\beta_j$ very near 0" is also plausible, and that the distribution of the effects will be unimodal about 0. 
Alternatively, we can motivate A1 by its effect on point estimates, which is to ``shrink" the estimates towards the mode - 
such shrinkage is desirable from several standpoints for improving estimation accuracy. 
Note that assumption A1 relates to the distribution of {\it all} effects, and not only the {\it detectable} effects (i.e.~those that are significantly different from zero). It is very likely that the distribution of {\it detectable} non-zero effects will be multimodal, with one mode for detectable positive effects and another for detectable negative effects, and A1 does not contradict this.

Interestingly, although the unimodal assumption A1 seems natural, much previous related work on estimating False Discovery Rates  
has assumed, either explicitly or implicitly, that the effect sizes are multimodal (see Results for more details). 
In contrast, almost all analogous work in large-scale regression assumes
a unimodal prior distribution for the effect sizes, common choices being the spike and slab, Laplace, $t$, normal-gamma, normal-inverse-gamma, or horseshoe priors.
One of our aims here is to emphasize potential benefits of also making the unimodal assumption in the FDR context.

Assumption A2 can derived from (\ref{eqn:beta hat}) plus a couple of other assumptions. Specifically, assume that a) $\hat\beta_j, s_j$ contain most of the information about $\beta_j$ in the data $D_j$ (i.e. they are ``approximately sufficient" for $D_j$) and that b) $s_j$ alone contains little information about $\beta_j$. The former (a) suggests the approximation $\hat{L}_j(\beta_j) \propto p(\hat\beta_j, s_j | \beta) = p(\hat\beta | \beta, s_j) p(s_j | \beta)$, while the latter (b) suggests assuming that $p(s_j|\beta_j)$ does not depend on $\beta_j$. Putting these two together yields $\hat{L}_j(\beta_j) \propto p(\hat\beta_j | \beta, s_j)$, which, with (\ref{eqn:betahat}),  implies A2. If $\hat\beta_j, s_j$ are not sufficient for $D_j$ then there is some loss of efficiency in making this approximation, but all Bayesian inferences remain valid provided they are interpreted as conditional on $\hat\beta_j,s_j$, rather than conditional on $D_j$. See \cite{johnson.xx} and \cite{wakefield.xx} for more general discussion and examples of Bayesian inference based on summary statistics.

Alternatively A2 could be considered definitional for $\hat\beta_j,s_j$: that is, choose $\hat\beta_j,s_j$ such that A2 holds.
